Quality Definitions of Qualities

### 2021-11-17 StateOfPractice/Papers/MedImageSoft_SOP/MedImageSoft_SOP_AcademicRadiology.tex
Updates for Med Image SOP up to section 2 (background)

\documentclass[preprint,12pt,authoryear]{elsarticle}

@@

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{mindmap}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{arydshln}

@@

\pgfplotsset{compat=1.13}

@@

To gain insights, we devised five research questions, which can be applied
to MI, and to other domains, of research software \citep{SmithEtAl2021}:

@@

\item[RQ1.] \hypertarget{rq1}What artifacts are present in current software
projects? What role does documentation play in the projects? What are the
developers' attitude toward it?
\item[RQ2.] \hypertarget{rq2}What tools are used in the development of current
software packages?
\item[RQ3.] \hypertarget{rq3}What principles, processes, and methodologies are
used in the development of current software packages?
\item[RQ4.] \hypertarget{rq4}What are the pain points for developers working on
research software projects? What aspects of the existing processes,
methodologies, and tools do they consider as potentially needing improvement?
What changes to processes, methodologies, and tools can improve software
development and software quality?
\item[RQ5.] \hypertarget{rq5}What is the current status of the following
software qualities for the projects? What actions have the developers taken to
address them?
\begin{itemize}
	\item Installability
	\item Correctness \& Verifiability
	\item Reliability
	\item Robustness
	\item Usability
	\item Maintainability
	\item Reusability
	\item Understandability
	\item Visibility/Transparency
	\item Reproducibility
\end{itemize}
\item[RQ6.] \hypertarget{rq6}How does software designated as high quality by
this methodology compare with top-rated software by the community?
\end{description}

\subsection{Overview of the Methodology}

We designed a general methodology to assess the state of the practice for SC
software \citep{SmithEtAl2021}. Details can be found in Section~\ref{}.  This
methodology builds off prior work to assess the state of the practice for such
domains as Geographic Information Systems \citep{smith2018state}, Mesh
Generators \citep{smith2016state}, Seismology software
\citep{Smith2018Seismology}, and Statistical software for psychology
\citep{smith2018statistical}.  In keeping with the previous methodology, we have
maintained the constraint that the work load for measuring a given domain should
be feasible for a team as small as one person, and for a short time,
ideally around a person month of effort. A person month is considered to be $20$
working days ($4$ weeks in a month, with $5$ days of work per week) at $8$
person hours per day, or $20 \cdot 8 = 160$ person hours.

With our methodology, we first choose an SC domain (in the current case MI) and
identify a list of about 30 software packages. We approximately measure the
qualities of each package by filling in a grading template (forward ref?).
Compared with our previous methodology, the new methodology also includes
repository based metrics, such as the number of files, number of lines of code,
percentage of issues that are closed, etc. (forward ref?).  With the
quantitative data in the grading template, we rank the software with the
Analytic Hierarchy Process (AHP) (forward ref?). After this, as another addition
to our previous methodology, we interview some of the development teams to
further understand the status of their development process (forward ref?).
Finally, we summarize the results and propose recommendations for future SC
software development (forward ref?).

@@

We need to restrict the scope of MI software that we consider so that the
measurement exercise is feasible within a person month of effort. MI considers a
broad range of different problems.  According to \citet{Bankman2000}, MI
software deals with six different basic problems, while \citet{Angenent2006}
pointed out that four fundamental problems are solved by MI software. While both
mentioned Segmentation, Registration, and Visualization of medical images,
Bankman also included Enhancement, Quantification, and three functions for MI
archiving and telemedicine systems (Compression, Storage, and Communication)
\citep{Bankman2000}. On the other hand, \citet{Angenent2006} included
Simulation. According to Wikipedia contributors \citep{enwiki:1034877594}, MI
software has primary functions in Segmentation, Registration, Visualization
(including the basic display, reformatted views, and 3D volume rendering),
Statistical Analysis, and Image-based Physiological Modelling. As
\citet{Kim2011} describes, the general steps of medical image analysis after
obtaining digital data include Enhancement, Segmentation, Feature Extraction,
Classification, and Interpretation. Besides the above major functions, some MI
software provides supportive functions. For example, with Tool Kit libraries VTK
\citep{SchroederEtAl2006} and ITK \citep{McCormick2014}, developers build
software with Visualization and Analysis functions; Picture Archiving and
Communication System (PACS) helps users to economically store and conveniently
access images \citep{Choplin1992}.

Based on our literature survey, we divided MI software into five sub-groups and
several sub-sub-groups by their major functions, as shown in Figure
\ref{fig_mi_functions}.

\begin{figure}[ht]
\centering
\begin{tikzpicture}[mindmap, grow cyclic, every node/.style=concept, concept
color=orange!40,
level 1/.append style={level distance=5cm,sibling angle=72},
level 2/.append style={level distance=3cm,sibling angle=90},
level 3/.style={level distance=2.3cm,sibling angle=90}]
\node{MI software}
child[concept color=teal!40] { node {Enhancement}}
child[concept color=teal!40] { node {Analysis}
    child[concept color=blue!30] { node {Registration}}
    child[concept color=blue!30,] { node {Segmentation}}
    child[concept color=blue!30] { node {Statistical Analysis}
    child[concept color=blue!20] { node {Feature Extraction}}
    child[concept color=blue!20] { node {Classification}}
    child[concept color=blue!20] { node {Interpretation}}
    }}
child[concept color=teal!40] { node {Simulation/\\Modeling}}
child[concept color=teal!40] { node {Supporting}
    child[concept color=blue!30] { node {Tool Kit}}
    child[concept color=blue!30] { node {PACS}}
}
child[concept color=teal!40] { node {Visualization}
    child[concept color=blue!30] { node {2D Display}}
    child[concept color=blue!30] { node {3D Rendering}}
    child[concept color=blue!30] { node {Reformatted Views}}
};
\end{tikzpicture}
\caption{Major functions of MI software}
\label{fig_mi_functions}
\end{figure}

To keep the data collection and analysis feasible, we limited the scope of the
software to the software packages providing the Visualization tools and
functions in this project.

[Roadmap - instead sprinkle forward references throughout the introduction?]

@@

When designing a method for evaluating the state of the practice of
domain-specific software, we included a step to select domain and software.
Knowledge of different software categories is essential for the selection. To
compare and rank the software qualities with the grading template in Appendix
\ref{ap_grading_template}, we need the definitions of qualities and the AHP.

In this section, we introduce the relevant software categories (Section
\ref{sec_software_categories}). We also cover the software quality definitions
(Section \ref{sec_software_quality}) and an overview of the AHP (Section
\ref{sec_AHP}).

@@

We target specific software categories to narrow down the scope when selecting
software packages for measuring. One way to categorize them is grouping by
functions, such as analyzing the scope for the MI software (Section
\ref{sec_scope}), which requires specific domain knowledge. In this section, we
discuss three common software categories that we can apply to all SC domains:
Open source software (OSS), freeware, and commercial software.

\subsubsection{Open Source Software} \label{sec_open_source_software}

For OSS, the source code is openly accessible. Users have the right to study,
change and distribute it under a license granted by the copyright holder. For
many OSS projects, the development process relies on the collaboration of
different contributors worldwide \citep{Corbly2014}. Accessible source code
usually exposes more ``secrets'' of a software project, such as the underlying
logic of software functions, how developers achieve their works, and the flaws
and potential risks in the final product. Thus, it brings much more convenience
to researchers analyzing the qualities of the project.

\subsubsection{Freeware} \label{sec_freeware}

Freeware is software that can be used free of charge. Unlike with OSS, the
authors of freeware do not allow users to access or modify the source code of
the software \citep{LINFO2006}. The term \textit{freeware} should not be confused
with \textit{free software}, which is similar to OSS. To the end-users, the
differences between freeware and OSS often do not bother them. The fact that
these products are free of charge is likely to make them popular with many
users. However, software developers, end-users who wish to modify the source
code, and researchers looking for insight into software development process will
find the inaccessible source code a problem.

\subsubsection{Commercial Software}

``Commercial software is software developed by a business as part of its
business'' \citep{GNU2019}. Typically speaking, the users are required to pay to
access all of the features of commercial software, excluding access to the
source code. However, some commercial software is also free of charge
\citep{GNU2019}. Based on our experience, most commercial software products are
not OSS.

For some specific software, the backgrounds of commercial software developers
often differ from the ones of non-commercial OSS. In such a case, the former is
usually the product of software engineers, and the latter is likely to have
developers who work in the domain and are also end-users of the products. One
example of such software is SC software, since the developers need to utilize
their domain-specific during the development process \citep{Wilson2014}.

@@

This section lists the definitions of 10 software qualities, which are from
Smith et al. \citep{SmithEtAl2020}. We aim to measure each of them for selected
SC software packages. The order of the first nine qualities follows our grading
template in Appendix \ref{ap_grading_template}. We do not measure
\textit{reproducibility} with the grading template, but discuss it with the
developers by interviews.

\begin{itemize}
	\item \textbf{Installability} The effort required for the installation,
	uninstallation, or reinstallation of a software or product in a specified
	environment \citep{ISO/IEC25010} \citep{lenhard2013measuring}.

	\item \textbf{Correctness \& Verifiability} A program is correct if it
	behaves according to its stated specifications. Verifiability is the extent
	to which a set of tests can be written and executed, to demonstrate that the
	delivered system meets the specification \citep{GhezziEtAl2003}.

@@

To generate ranking scores for a set of software packages, we use AHP, which
utilizes pairwise comparisons between all of the packages. Thomas L. Saaty
developed this tool, and people widely used it to make and analyze multiple
criteria decisions \citep{VaidyaEtAl2006}. AHP organizes multiple criteria
factors in a hierarchical structure and uses pairwise comparisons between
alternatives to calculate relative ratios \citep{Saaty1990}.

For a project with $ m $ criteria, we can use an $m\times m$ matrix $A$ to
record the relative importance between factors. When comparing criterion $i$ and
criterion $j$, the value of $A_{ij}$ is decided as follows, and the value of
$A_{ji}$ is $1/A_{ij}$ \citep{Saaty1990},

\begin{itemize}
	\item $A_{ij} = 1$ if criterion $i$ and criterion $j$ are equally important;
	\item $A_{ij} = 9$ if criterion $i$ is extremely more important than
	criterion $j$;
	\item $A_{ij}$ equals to an integer value between 1 and 9 according the the
	relative importance of criterion $i$ and criterion $j$.
\end{itemize}

The above process assumes that criterion $i$ is not less important than
criterion $j$, otherwise, we need to reverse $i$ and $j$ and determine $A_{ji}$
first, then $A_{ij} = 1/A_{ji}$.

The priority vector $w$ can be calculated by solving the following equation
\citep{Saaty1990}, 
\begin{equation} 
    Aw = \lambda_{max}w,
\end{equation}
where $\lambda_{max}$ is the maximal eigenvalue of $A$.

In this project, $w$ is approximated with the classic \textit{mean of normalized
values} approach \citep{AlessioEtAl2006},

@@

Suppose there are $n$ alternatives, for criterion $i = 1, 2, ... , m$, we can
create an $n\times n$ matrix $B_i$ to record the relative preferences between
these choices. The way of generating $B_i$ is similar to the one for $A$.
However, unlike comparing the importance between criteria, we pairwise decide
how much we favor one alternative over the other. We use the same method to
calculate the local priority vector for each $B_i$.

In this project, the first nine software qualities mentioned in Section
\ref{sec_software_quality} are the criteria ($m = 9$), while 29 software
packages ($n = 29$) are compared for each of the $m$ criteria. The software are
evaluated with the grading template in Appendix \ref{ap_grading_template} and a
subjective score from one to ten is given for each quality for each package. For
each quality, for a pair of packages $i$ and $j$, such that $score_i >=
score_j$, the difference between two scores is $\mathit{diff_{ij}} = score_i -
score_j$. The relationship between $A_{ij} = 1$ and $\mathit{diff_{ij}}$ is as
follows:

@@

Thus, we approximate the pairwise comparison result of $i$ versus $j$ by the
following equation:

\begin{equation}
A_{ij} = min(score_i - score_j + 1, 9)
\end{equation}

@@

We grade the selected software using a template (Section
\ref{sec_grading_template}) and a specific empirical method (Section
\ref{sec_empirical_measurements}). Some technical details for the measurements
are in Section \ref{sec_technical_details}.

>>>>

%\documentclass[preprint,12pt,authoryear]{elsarticle}
\documentclass[3p, 12pt,authoryear]{elsarticle}

@@

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsmath,amsthm}

@@

\usepackage{hyperref}
%\usepackage{tikz}
%\usetikzlibrary{mindmap}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{arydshln}

@@

%\pgfplotsset{compat=1.13}

@@

To gain insights, we devised five research questions, which can be applied
to MI, as well as to other domains, of research software \citep{SmithEtAl2021}:

@@

\item[RQ1.] \hypertarget{rq1}What artifacts are present in current software
projects? What role does documentation play in the projects? What are the
developers' attitude toward it?
\item[RQ2.] \hypertarget{rq2}What tools are used in the development of current
software packages?
\item[RQ3.] \hypertarget{rq3}What principles, processes, and methodologies are
used in the development of current software packages?
\item[RQ4.] \hypertarget{rq4}What are the pain points for developers working on
research software projects? What aspects of the existing processes,
methodologies, and tools do they consider as potentially needing improvement?
What changes to processes, methodologies, and tools can improve software
development and software quality?
\item[RQ5.] \hypertarget{rq5}What is the current status of the following
software qualities for the projects? What actions have the developers taken to
address them?  (Section~\ref{ch_background} provides definitions of the software
qualities.)
\begin{itemize}
	\item Installability
	\item Correctness \& Verifiability
	\item Reliability
	\item Robustness
	\item Usability
	\item Maintainability
	\item Reusability
	\item Understandability
	\item Visibility/Transparency
	\item Reproducibility
\end{itemize}
\item[RQ6.] \hypertarget{rq6}How does software designated as high quality by
this methodology compare with top-rated software by the community?
\end{description}

@@

We need to restrict the scope of MI software that we consider so that the
measurement exercise is feasible within the targeted person month of effort. We
can restrict the scope by selecting a sub-set of the broad range of problems
considered by MI.  Summing the sets of MI tasks from \citet{Bankman2000} and
\citet{Angenent2006}, we have the following problems are solved by MI software:
Segmentation, Registration, Visualization, Enhancement, Quantification,
Simulation, plus three functions for MI archiving and telemedicine systems
(Compression, Storage, and Communication). To this list Wikipedia contributors
\citep{enwiki:1034877594} add Statistical Analysis and Image-based Physiological
Modelling. \citet{Kim2011} adds Feature Extraction, Classification, and
Interpretation. Besides the above major functions, some MI software provides
supportive functions. For example, using Tool Kit libraries VTK
\citep{SchroederEtAl2006} and ITK \citep{McCormick2014}, developers build
software with Visualization and Analysis functions. Finally, Picture Archiving
and Communication System (PACS) helps users to economically store and
conveniently access images \citep{Choplin1992}.

Based on our literature survey, we divided MI software into five sub-groups and
several sub-sub-groups by their major functions, as shown in
Figure~\ref{fig_mi_functions}. We selected the sub-group of Visualization for
the current state of the practice exercise.

\begin{figure}[ht]
\centering
\includegraphics[scale=0.6]{figures/FunctionsOfMiSoftware.pdf}
\caption{Major functions of MI Software} \label{fig_mi_functions}
\end{figure}

% \begin{figure}[ht]
% \centering
% \begin{tikzpicture}[mindmap, grow cyclic, every node/.style=concept, concept
% color=orange!40,
% level 1/.append style={level distance=5cm,sibling angle=72},
% level 2/.append style={level distance=3cm,sibling angle=90},
% level 3/.style={level distance=2.3cm,sibling angle=90}]
% \node{MI software}
% child[concept color=teal!40] { node {Enhancement}}
% child[concept color=teal!40] { node {Analysis}
%     child[concept color=blue!30] { node {Registration}}
%     child[concept color=blue!30,] { node {Segmentation}}
%     child[concept color=blue!30] { node {Statistical Analysis}
%     child[concept color=blue!20] { node {Feature Extraction}}
%     child[concept color=blue!20] { node {Classification}}
%     child[concept color=blue!20] { node {Interpretation}}
%     }}
% child[concept color=teal!40] { node {Simulation/\\Modeling}}
% child[concept color=teal!40] { node {Supporting}
%     child[concept color=blue!30] { node {Tool Kit}}
%     child[concept color=blue!30] { node {PACS}}
% }
% child[concept color=teal!40] { node {Visualization}
%     child[concept color=blue!30] { node {2D Display}}
%     child[concept color=blue!30] { node {3D Rendering}}
%     child[concept color=blue!30] { node {Reformatted Views}}
% };
% \end{tikzpicture}
% \caption{Major functions of MI software}
% \label{fig_mi_functions}
% \end{figure}

\subsection{Methodology Overview}

We designed a general methodology to assess the state of the practice for SC
software \citep{SmithEtAl2021}. Details can be found in
Section~\ref{ch_methods}.  This methodology builds off prior work to assess the
state of the practice for such domains as Geographic Information Systems
\citep{smith2018state}, Mesh Generators \citep{smith2016state}, Seismology
software \citep{Smith2018Seismology}, and Statistical software for psychology
\citep{smith2018statistical}.  In keeping with the previous methodology, we have
maintained the constraint that the work load for measuring a given domain should
be feasible for a team as small as one person, and for a short time, ideally
around a person month of effort. A person month is considered to be $20$ working
days ($4$ weeks in a month, with $5$ days of work per week) at $8$ person hours
per day, or $20 \times 8 = 160$ person hours.

With our methodology, we first choose an SC domain (in the current case MI) and
identify a list of about 30 software packages. (For measuring MI we used 29
software packages.)  We approximately measure the qualities of each package by
filling in a grading template. Compared with our previous methodology, the new
methodology also includes repository based metrics, such as the number of files,
number of lines of code, percentage of issues that are closed, etc.  With the
quantitative data in the grading template, we rank the software with the
Analytic Hierarchy Process (AHP) (Details are found in
Section~\ref{ch_background}). After this, as another addition to our previous
methodology, we interview some of the development teams to further understand
the status of their development process. Finally, we summarize the measurements
(Section~\ref{ch_results}), summarize the interview answers
(Section~\ref{ch_interview}), answer the research questions
(Section~\ref{ch_answers}) and propose recommendations
(Section~\ref{ch_recommendations}) for future SC software development.

@@

In this section, we introduce the relevant software categories (Section
\ref{sec_software_categories}). The categories will be used when collecting and
assessing the software packages.  We also review the definitions of software
qualities (Section \ref{sec_software_quality}) and provide an overview of the
AHP (Section \ref{sec_AHP}).

@@

When assessing software packages, we need to know what license the software is
distributed under.  In particular, we need to know whether the source code will
be available to us or not.  In this section, we present three common software
categories:

\item \textbf{Open Source Software (OSS)} For OSS, the source code is openly
accessible. Users have the right to study, change and distribute it under a
license granted by the copyright holder. For many OSS projects, the development
process relies on the collaboration of different contributors worldwide
\citep{Corbly2014}. Accessible source code usually exposes more ``secrets'' of a
software project, such as the underlying logic of software functions, how
developers achieve their works, and the flaws and potential risks in the final
product. Thus, it brings much more convenience to researchers analyzing the
qualities of the project.

\item \textbf{Freeware} Freeware is software that can be used free of charge.
Unlike with OSS, the authors of do not allow users to access or modify the
source code \citep{LINFO2006}. To many end-users, the differences between
freeware and OSS may not be relevant. However, software developers, end-users
who wish to modify the source code, and researchers looking for insight into
software development process may find the inaccessible source code a problem.

\item \textbf{Commercial Software} ``Commercial software is software developed
by a business as part of its business'' \citep{GNU2019}. Typically speaking, the
users are required to pay to access all of the features of commercial software,
excluding access to the source code. However, some commercial software is also
free of charge \citep{GNU2019}. Based on our experience, most commercial
software products are not OSS.

@@

Quality is defined as a measure of the excellence or worth of an entity.  As is
common practice, we do not think of quality as a single measure, but rather as a
set of measures.  That is, quality is a collection of different qualities, often
called ``ilities.''  Below we list the 10 qualities of interest for this study,
as summarized in \citet{SmithEtAl2021-QDef}.  The order of the qualities follows
the order used in \cite{GhezziEtAl2003}, which puts related qualities (like
correctness and reliability) together.  Moreover, the order is roughly the same
as the order qualities are considered in practice.  [*** To be completed - not
currently in sync with QDef paper, QDef paper not completely done ***]

\begin{itemize}
	\item \textbf{Installability} The effort required for the installation
    and/or uninstallation of software in a specified environment.

	\item \textbf{Correctness \& Verifiability} A program is correct if it
    matches its specification.  The specification can either be explicitly or
    implicitly stated.  Verifiability is the extent to which the software
    components or the integrated product can be evaluated to demonstrate whether
    the system functions as expected.

@@

AHP is used to generate a ranking for a set of software packages. Thomas L.\
Saaty developed AHP in the 1970s, and people have widely used it since to make
and analyze multiple criteria decisions \citep{VaidyaEtAl2006}. AHP organizes
multiple criteria factors in a hierarchical structure and uses pairwise
comparisons between alternatives to calculate relative ratios \citep{Saaty1990}.

For a project with $m$ criteria, we can use an $m\times m$ matrix $A$ to record
the relative importance between factors. When comparing criterion $i$ and
criterion $j$, the value of $A_{ij}$ is decided as follows, with the value of
$A_{ji}$ generally as $1/A_{ij}$ \citep{Saaty1990}.  $A_{ij} = 1$ if criterion
$i$ and criterion $j$ are equally important, while $A_{ij} = 9$ if criterion $i$
is extremely more important than criterion $j$.  The natural numbers between 1
and 9 are used to show the different levels of relative importance between these
two extremes. The above assumes that criterion $i$ is not less important than
criterion $j$.  If that is not the case, we reverse $i$ and $j$ and determine
$A_{ji}$ first, then $A_{ij} = 1/A_{ji}$.

The priority vector $w$, which ranks the criteria by their importance, can be
calculated by solving the equation \citep{Saaty1990}:
\begin{equation} 
    A w = \lambda_{max} w,
\end{equation}
where $\lambda_{max}$ is the maximal eigenvalue of $A$.  In this project, $w$ is
approximated with the classic \textit{mean of normalized values} approach
\citep{AlessioEtAl2006}:

@@

If there are $n$ alternatives, for criterion $i = 1, 2, ... , m$, we can create
an $n\times n$ matrix $B_i$ to record the relative preferences between these
choices for each criterion. The way of generating $B_i$ is similar to the one
for $A$. However, rather than comparing the importance between criteria, we
pairwise decide how much we favor one alternative over the other. We use the
same method to calculate the local priority vector for each $B_i$.  The local
priority vector in this case ranks the $n$ alternatives for criterion $i$.

In this project, the first nine software qualities mentioned in Section
\ref{sec_software_quality} are the criteria ($m = 9$), while 29 software
packages ($n = 29$) are compared for each of the $m$ criteria. The software are
evaluated with the grading template in Section~\ref{sec_grading_template}, which
includes a subjective score from $1$ to $10$ for each quality for each package.
For each quality, for a pair of packages $i$ and $j$, with $\mathit{score}_i >=
\mathit{score}_j$, the difference between the two scores is $\mathit{diff_{ij}}
= \mathit{score}_i - \mathit{score}_j$. The mapping between $\mathit{diff_{ij}}$
(which can vary between 0 and 9) and the values in $A_{ij}$ (which can vary
between 1 and 9) is as follows:

@@

\noindent Thus, we approximate the pairwise comparison result of $i$ versus $j$
by the following equation:

\begin{equation}
A_{ij} = \text{min}(\mathit{score}_i - \mathit{score}_j + 1, 9)
\end{equation}

@@

We grade the selected software using a template (Section
\ref{sec_grading_template}) and a specific empirical method (Section
\ref{sec_empirical_measurements}). Some technical details for the measurements
are in Section \ref{sec_technical_details}.  We do not measure
\textit{reproducibility} with the grading template, but discuss it with the
developers by interviews.

### 2021-11-17 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Updates for Med Image SOP up to section 2 (background)

\begin{mybox}
\subsubsection*{Verifiability} Definition~\ref{Defn_Verifiability1}
rephrased: Verifiability is the extent to which a set of tests can be
written and executed, to demonstrate that the delivered system meets the
specification.
\end{mybox}

>>>>

\begin{mybox}
\subsubsection*{Verifiability} The extent to which software components or the
integrated product can be evaluated to demonstrate whether the system functions
as expected \citep{wiegers2003softreq}.

Definition~\ref{Defn_Verifiability1}
rephrased: Verifiability is the extent to which a set of tests can be
written and executed, to demonstrate that the delivered system meets the
specification.
\end{mybox}
